\vspace{-2cm}A generative model for urban firm networks

### 2022-05-12 Response_to_reviewers.tex

	\medskip

%2.3 -

	\item \textit{The model is ambiguously described. The link probability update $p_{ij}$ is between 0 and 1, does it mean that 1) at each time step each link ij has a $p_{ij}$ probability to be updated or that 2) like in the preferential attachment model, only one link is updated at each time step (and thus the real probability is $p_ij/sum_{lk}(p_{lk})$)?}

	$\rightarrow$ There was a lack of clarity in the description of the link addition process: the provided function is an utility and the probability is computed accordingly by renormalising it. A single link is updated at each time step. This was reformulated.

@@

	$\rightarrow$ This was added in model description.

	\medskip

	\item \textit{Link creation probability formula - industrial proximity: oversight to remove k (should not depend on k).}

	$\rightarrow$ This was corrected using a matrix notation for industrial structure.

@@

	$\rightarrow$ This sentence was unclear, we meant that fit improvement in model 4 was not due to overfitting compared to other models. This was reformulated.

	\medskip

	\item \textit{Model exploration: The variation of community size was explored but the indicator has not been defined.}

	$\rightarrow$ This additional indicator was added in model description.

@@

	$\rightarrow$ The paper positioning and goal were reframed. The purpose is to introduce a generative model to understand how different geographical and economic factors influence the growth of urban firm networks, with both potentialities for theoretical explanations (through exploration and calibration) and practical applications (the latest being a proof-of-concept in this work).

	\medskip

%2.
	\item \textit{Clarify the jargon. What is a 'generative model'? What is 'synthetic' data?}

	$\rightarrow$ Specific terms were better defined and the paper was screened for clarity.

@@

	$\rightarrow$ This has been better explained in the literature review and introduction.

	\medskip

%3)
	\item \textit{More information on why the synthetic and real world models have been set up are needed. What do they bring to our understandings? You mention how internationalisation, metropolisation, fit within the model .... but what about regionalisation and specialisation? Are these latter just an outcome of the analysis, whilst the former are model parameters? Then why are they treated as the same in the introduction?}

	$\rightarrow$ Regionalisation and specialisation indicators where explored in a previous version of the model, but did not seem to bear significant information and were difficult to interpret, so these were removed from model description as they are not used. Regarding model setup, an extensive description of the synthetic setup is given in supplementary material.

@@

	\medskip

%4)
	\item \textit{Why in the statistical analysis do you then look at the 'most determining geo-economic factors influencing the creation of links between cities' - there was not real literature review to identify these - how do you then identify them? What is the relationship to the research question? Also pg 6 again describe the processes driving the networks (from pg 2 as noted above) - but these measures where not really discussed in when the model was being explained. How do they fit?}

	$\rightarrow$ The literature on geo-economic factors has been enhanced, and some references suggesting candidate processes are included in model rationale.

### 2022-05-12 S2_Text.tex
Update on Overleaf.

\section*{S2 Text: Model setup and sensitivity analysis}

@@

@@

\section*{Sensitivity analysis}

@@

%%%%%%%%%%%%%
\begin{table}[h!]
\begin{adjustwidth}{-2.25in}{0in}
\caption{Saltelli sensitivity indices, for indicators in rows and parameters in columns. We give for each pair the first order index (F) and the total order index (T).\label{tab:saltelli}}
\hspace{-1cm}\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|c|c|c|}
\hline
 & \multicolumn{2}{|c|}{$\gamma_G$} & \multicolumn{2}{|c|}{$\gamma_D$} & \multicolumn{2}{|c|}{$\gamma_S$} & \multicolumn{2}{|c|}{$\gamma_W$} & \multicolumn{2}{|c|}{$\gamma_O$} & \multicolumn{2}{|c|}{$\gamma_D$} \\
 & F & T & F & T & F & T & F & T & F & T & F & T \\
 \hline
Internationalisation & 0.2 & 0.3 & 0.7 & 0.7 & 0.001 & 0.009 & $4\cdot 10^{-4}$ & 0.007 & 0.03 & 0.04 & 0.02 & 0.04 \\
Metropolisation & 0.02 & 0.1 & 0.02 & 0.2 & 0.002 & 0.1 & 0.001 & 0.09 & 0.2 & 0.6 & 0.3 & 0.6 \\
Modularity & 0.3 & 0.4 & 0.6 & 0.6 & 0.004 & 0.02 & $3\cdot 10^{-4}$ & 0.01 & 0.005 & 0.03 & 0.002 & 0.03 \\
Avg. com. size & 0.008 & 0.09 & 0.01 & 0.1 & 0.002 & 0.07 & 0.003 & 0.04 & 0.3 & 0.6 & 0.4 & 0.6 \\
Degree entropy & 0.006 & 0.02 & 0.003 & 0.02 & 0.006 & 0.03 & 0.008 & 0.02 & 0.5 & 0.5 & 0.5 & 0.5 \\
Weight entropy & 0.04 & 0.1 & 0.03 & 0.1 & 0.008 & 0.08 & 0.01 & 0.07 & 0.4 & 0.5 & 0.4 & 0.5 \\\hline
\end{tabular}
\end{adjustwidth}
\end{table}
%%%%%%%%%%%%%

>>>>

\section*{S2 Text: Statistical models, generative model setup and sensitivity analysis}

@@

\subsection*{Zero-inflated models}

We show in Table~\ref{tab:zeroinfl} estimation results for zero-inflated and hurdle statistical models. We only show models with all variables included, which had the best AIC values. Main model coefficients are very close in both approaches, and do not deviate largely from values obtained with the simpler model. All coefficients have a high significance in this case. Regarding the additional components, both give the same qualitative outcome (with opposite signs, the hurdle interpretation being the opposite of the zero-inflated). Distance increase the likelihood of having a zero flow, while other variables decrease it, with the same order of magnitude of effect size than the main component. R-squared values are much lower than simpler model, since a large proportion of the dataset are zeros and the models are thus harder to fit when including them.

%%%%%%%%%%%%%
\begin{table}[!ht]
\begin{adjustwidth}{-1in}{0in}
\caption{{\bf Zero-inflated and Hurdle statistical models.}\label{tab:zeroinfl}}
\medskip
\begin{tabular}{|l|c|c|c|c|}
\hline
Model  & \multicolumn{2}{|c|}{Zero-inflated} & \multicolumn{2}{|c|}{Hurdle} \\ 
 & Count & Zero-infl. & Count & Zero-hurdle \\
\hline
$\log(d_{ij})$ &    -0.28*** (7e-4) &   0.88*** (0.01)      &   -0.29*** (8e-6)   &  -0.75*** (0.01)    \\
$\log(T_i)$ & 0.74*** (4e-6)  & -0.74*** (7e-3)       &   0.74***  (5e-6)     &  0.67*** (5e-3)   \\
$\log(T_j)$ & 0.64*** (4e-6)  & -0.52*** (7e-3)      &    0.64***  (4e-6)     &  0.48*** (5e-3)    \\
$\log(s_{ij})$ & 0.46*** (2e-5)   &  -0.33*** (3e-2)  &  0.45*** (2e-5)       &  0.27*** (0.02)    \\
\hline
$R^2$ &   \multicolumn{2}{|c|}{0.1607}     &  \multicolumn{2}{|c|}{0.1661}  \\
%MSE & & \\
AIC &     \multicolumn{2}{|c|}{5.85e10}    &   \multicolumn{2}{|c|}{5.85e10}  \\
\hline
\end{tabular}
\end{adjustwidth}
\end{table}
%%%%%%%%%%%%%

%pscl::hurdle(formula = intweight ~ log(distance) + log(from_turnover) + log(to_turnover) + 
%    log(sim), data = dz, dist = "poisson", zero.dist = "poisson")
%
%Pearson residuals:
%       Min         1Q     Median         3Q        Max 
%-9.195e+03 -1.373e-01 -7.627e-02 -4.204e-02  1.727e+04 
%
%Count model coefficients (truncated poisson with log link):
%                     Estimate Std. Error z value Pr(>|z|)    
%(Intercept)        -9.853e+00  1.345e-04  -73252   <2e-16 ***
%log(distance)      -2.875e-01  7.603e-06  -37812   <2e-16 ***
%log(from_turnover)  7.379e-01  4.708e-06  156720   <2e-16 ***
%log(to_turnover)    6.379e-01  4.060e-06  157119   <2e-16 ***
%log(sim)            4.550e-01  2.137e-05   21292   <2e-16 ***
%Zero hurdle model coefficients (censored poisson with log link):
%                     Estimate Std. Error z value Pr(>|z|)    
%(Intercept)        -20.525823   0.155298 -132.17   <2e-16 ***
%log(distance)       -0.747788   0.010991  -68.04   <2e-16 ***
%log(from_turnover)   0.665678   0.005630  118.23   <2e-16 ***
%log(to_turnover)     0.479214   0.005707   83.96   <2e-16 ***
%log(sim)             0.278290   0.022439   12.40   <2e-16 ***
%---
%Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1 
%
%Number of iterations in BFGS optimization: 46 
%Log-likelihood: -2.927e+10 on 10 Df

% 0.1661997

%mean((dz$intweight-hurdle2$fitted)^2)
%[1] 6.119694e+12

% > AIC(hurdle2)
%[1] 58545461912

%pscl::zeroinfl(formula = intweight ~ log(distance) + log(from_turnover) + log(to_turnover) + 
%    log(sim), data = dz, dist = "poisson")
%
%Pearson residuals:
%       Min         1Q     Median         3Q        Max 
%-7.693e+00 -1.335e-01 -6.957e-02 -3.591e-02  1.760e+04 
%
%Count model coefficients (poisson with log link):
%                     Estimate Std. Error z value Pr(>|z|)    
%(Intercept)        -9.853e+00  1.345e-04  -73251   <2e-16 ***
%log(distance)      -2.875e-01  7.603e-06  -37810   <2e-16 ***
%log(from_turnover)  7.379e-01  4.708e-06  156719   <2e-16 ***
%log(to_turnover)    6.379e-01  4.060e-06  157120   <2e-16 ***
%log(sim)            4.550e-01  2.137e-05   21294   <2e-16 ***
%
%Zero-inflation model coefficients (binomial with logit link):
%                    Estimate Std. Error z value Pr(>|z|)    
%(Intercept)        22.046685   0.180605  122.07   <2e-16 ***
%log(distance)       0.881724   0.013134   67.13   <2e-16 ***
%log(from_turnover) -0.737441   0.006776 -108.83   <2e-16 ***
%log(to_turnover)   -0.521642   0.006540  -79.76   <2e-16 ***
%log(sim)           -0.330340   0.025360  -13.03   <2e-16 ***
%---
%Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1 
%
%Number of iterations in BFGS optimization: 1 
%Log-likelihood: -2.927e+10 on 10 Df

% 0.1607349

%mean((dz$intweight-zinflpoisson2$fitted)^2)
%[1] 6.159803e+12

% AIC(zinflpoisson2)
%[1] 58545461691

@@

\subsection*{Sensitivity analysis}

@@

%%%%%%%%%%%%%
\begin{table}[h!]
\begin{adjustwidth}{-2.25in}{0in}
\caption{Saltelli sensitivity indices, for indicators in rows and parameters in columns. We give for each pair the first order index (F) and the total order index (T).\label{tab:saltelli}}
\hspace{-1cm}\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|c|c|c|}
\hline
 & \multicolumn{2}{|c|}{$d_0$} & \multicolumn{2}{|c|}{$c_0$} & \multicolumn{2}{|c|}{$\gamma_S$} & \multicolumn{2}{|c|}{$\gamma_W$} & \multicolumn{2}{|c|}{$\gamma_O$} & \multicolumn{2}{|c|}{$\gamma_D$} \\
 & F & T & F & T & F & T & F & T & F & T & F & T \\
 \hline
Internationalisation & 0.2 & 0.3 & 0.7 & 0.7 & 0.001 & 0.009 & $4\cdot 10^{-4}$ & 0.007 & 0.03 & 0.04 & 0.02 & 0.04 \\
Metropolisation & 0.02 & 0.1 & 0.02 & 0.2 & 0.002 & 0.1 & 0.001 & 0.09 & 0.2 & 0.6 & 0.3 & 0.6 \\
Modularity & 0.3 & 0.4 & 0.6 & 0.6 & 0.004 & 0.02 & $3\cdot 10^{-4}$ & 0.01 & 0.005 & 0.03 & 0.002 & 0.03 \\
Avg. com. size & 0.008 & 0.09 & 0.01 & 0.1 & 0.002 & 0.07 & 0.003 & 0.04 & 0.3 & 0.6 & 0.4 & 0.6 \\
Degree entropy & 0.006 & 0.02 & 0.003 & 0.02 & 0.006 & 0.03 & 0.008 & 0.02 & 0.5 & 0.5 & 0.5 & 0.5 \\
Weight entropy & 0.04 & 0.1 & 0.03 & 0.1 & 0.008 & 0.08 & 0.01 & 0.07 & 0.4 & 0.5 & 0.4 & 0.5 \\\hline
\end{tabular}
\end{adjustwidth}
\end{table}
%%%%%%%%%%%%%
